Generating Random Logic Programs Using Constraint Programming

### 2020-01-09 paper/paper.tex
It looks like counting is working!

\institute{University of Edinburgh, Edinburgh, UK\\
  Heriot-Watt University, Edinburgh, UK\\
  \email{p.dilkas@sms.ed.ac.uk}}
\maketitle

@@

Number of ways to fill $n$ positions with terms: % TODO: what's the smallest n?
\[
  P(n) = |\constants{}|^n + |\constants{}|^{n-1}|\variables{}| +
  \sum_{i=0}^{n-2} |\constants{}|^i \sum_{j=0}^{\min\{|\variables{}| - 1, n - i
    - 1\}} \binom{n-i-1}{j} (|\constants{}| + 1)^{n-i-j-1}
\]
where $i$ iterates over the number of constants before the first variable, and
$j$ iterates over the number of `new variable actions'. Explain:
$|\constants{}|+2$ possible actions.

>>>>

\institute{University of Edinburgh, Edinburgh, United Kingdom\\
  \email{p.dilkas@sms.ed.ac.uk}}
\maketitle

@@

Number of ways to fill $n$ positions with terms:
\[
  P(n) = |\constants{}|^n + \sum_{\substack{1 \le k \le |\variables{}|, \\ 0 =
      s_0 < s_1 < \dots < s_k < s_{k+1} = n+1}} \prod_{i=0}^k (|\constants{}| +
  i)^{s_{i+1} - s_i - 1}
\]
